### 2023-05-16 application.tex
sections
up

.
Let us consider the following four associated upward-closed sets.

@@

@@

>>>>

Let us consider the following four associated upward-closed sets.

@@

\cite{DBLP:journals/acta/ValkJ85} showed from a VASS $V$ how to construct another VASS $V'$ that has the property...

@@

\begin{theorem}
{\sc Resilience} is decidable for VASS when $\Safe$ is semilinear
and $\Bad = S \setminus \Safe$.
\end{theorem}

\begin{proof}
Hypothesis: $\Safe$ is semilinear, $\Bad = S \setminus \Safe$.
Then $\Bad$ is semilinear too.
{\sc Resilience} asks whether $\Bad \subseteq \pred^*(\Safe)$.
We have $\post^*(\Bad) \setminus \Safe = \Bad$ by extension of $S \setminus \Safe = \Bad$.
Thus $\post^*(\Bad) = \Bad \cup (\Safe \cap \post^*(\Bad))$. Since $(\Safe \cap \post^*(\Bad)) \subseteq \pred^*(\Safe)$, we have
$$\post^*(\Bad) \subseteq \pred^*(\Safe) \quad iff \quad \Bad \subseteq \pred^*(\Safe).$$
Since it is decidable whether $\post^*(\Bad) \subseteq \pred^*(\Safe)$ when 
$\Bad$ and $\Safe$ are both semilinear \cite{DBLP:journals/corr/abs-2207-02697}, 
{\sc Resilience} is decidable.
\end{proof}
